\documentclass[11pt, letterpaper]{article}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[margin=1in]{geometry}
\usepackage[sfdefault]{roboto}
\usepackage{xcolor}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{booktabs}
\frenchspacing
\usepackage{multicol}
\usepackage{eso-pic}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{setspace}
\usepackage{paralist}
\usepackage{quoting}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}

\usepackage{float}
\usepackage{bookmark}
\renewcommand{\thesection}{\arabic{section}.}
\renewcommand{\thesubsection}{\thesection\arabic{subsection}}
\renewcommand{\thesubsubsection}{\thesubsection.\arabic{subsubsection}}
\usepackage{etoolbox}
\patchcmd{\thebibliography}{\section*{\refname}}{\section{\refname}}{}{}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}

\begin{document}
\title{Introduction to Public Administration}

\author{CRJU/POSC 320 — Winter Intersession 2024-25}
\date{Asynchronous Online Course}

    \maketitle


\subsection*{Professor: David P. Adams, Ph.D.}

\subsubsection*{Contact Information:}

\begin{itemize}
	\item Office: 516 Gordon Hall
	\item Phone/SMS: (657) 278-4770
	\item website: \href{https://dadams.io}{\texttt{https://dadams.io}}
	\item email: \href{dpadams@fullerton.edu}{\texttt{dpadams@fullerton.edu}}
	\item Office Hours:
        \begin{itemize}
            \item Monday: 10:00 am -- 12:00 pm
            \item Schedule meetings throughout the week: \href{https://dadams.io/appt}{\texttt{https:dadams.io/appt}}
        \end{itemize}
\end{itemize}


\section*{Technical Problems}

\subsection*{University IT Help Desk}

Contact the instructor immediately to document the problem if you encounter any technical difficulties. Then contact the \href{http://www.fullerton.edu/it/students/helpdesk/index.php}{Student IT Help Desk} for assistance. You can also call the Student IT Help Desk at (657) 278-8888, \href{mailto:StudentITHelpDesk@fullerton.edu}{email}, visit them at the Pollak Library North \href{http://www.fullerton.edu/it/students/sgc/index.php}{Student Genius Center}, or log on to the \href{http://my.fullerton.edu/}{my.fullerton.edu} portal and click ``Online IT Help'' followed by ``Live Chat''.

\subsection*{Canvas Support}

If you encounter any technical difficulties with Canvas, call the Canvas Support Hotline at 855-302-7528, visit the \href{https://community.canvaslms.com/docs/DOC-10720-67952720329}{Canvas Community}, or click the ``Help'' button in the lower left corner of Canvas and select ``Report a Problem''. The \href{https://cases.canvaslms.com/liveagentchat?chattype=student&sfid=001A000000YzcwQIAR}{Student Support Live Chat} is available 24 hours a day, 7 days a week.

\section*{Response Time} I will strive to respond to all student emails and \emph{Canvas} messages within 24 hours, except on weekends and holidays. If you are still awaiting a response within 24 hours, please send a follow-up message. If you are still waiting to receive a response within 48 hours, please send another follow-up message and contact me via phone or SMS at (657) 278-4770.

\section*{Catalog Description}

Introduces public administration through current trends and problems of public sector agencies in such areas as organization behavior, public budgeting, personnel, planning and policy making. Examples and cases from the Criminal Justice field. (POSC 320 and CRJU 320 are the same course.)

\section*{Course Description}

Public administration plays an important role in our everyday lives. What do public administrators do? What makes this important field of government work? How are decisions made and how does the political environment impact those decisions? Our public administrators have to respond to various demands from United States residents and deal with situations and demands from abroad. The values we share interact and compete for the way our administrators create and implement policy. The core values of public administration include accountability, efficiency, and equity. We'll explore these topics and more as we engage in our class together. 

\vspace*{1em}

\noindent This course is an introduction to the study and practice---the science and art---of public administration. Students will be acquainted with the theoretical and practical aspects of public administration in the American political setting. Topics include organizational theory and practice, decision making, systems analysis, performance evaluation, and administrative and managerial improvement, among others. The emphasis is placed on understanding the roles and responsibilities of public administrators in a democratic political system. 
	

\section*{Student Learning Objectives}

\begin{enumerate}
    \item Display a broad understanding of public administration and its role in a democratic society. 

    \item Demonstrate knowledge of the concepts and theories in public administration. 
    
    \item Identify complex problems that face public organizations.

    \item Exhibit critical thinking by interpreting information, comparing ideas, and developing opinions. 
    
    \item Contrast public and private administration with their corresponding benefits and shortfalls. 

    \item Demonstrate effective written communication skills. 

\end{enumerate}

\section*{Required Text}

\begin{itemize}
    \item Kettl, Daniel F. 2023. \emph{Politics of the Administrative Process} (9th ed.) Washington, D.C.: CQ Press.
    \item Additional readings posted to Canvas
\end{itemize}

\section*{Prequisites}

POSC 100 and completion of G.E. Category D.1.  If you have not already taken and passed this course or its equivalent, you should not be enrolled in POSC/CRJU 320.

\section*{General Education Information}


\subsection*{Requirements Satisfied}

	This course satisfies General Education Explorations in Social Sciences subarea D.4 for those using Catalog Years 2018 and later. The writing assignments in this course, including the policy memo papers and current event summaries described below, meet the requirement of UPS 411.201: 
	\begin{quote}Writing assignments in General Education courses shall involve the organization and expression of complex data or ideas and careful and timely evaluations of writing so that deficiencies are identified, and suggestions for improvement and/or for means of remediation are offered. Evaluations of the student's writing competence shall determine the final course grade\ldots .\end{quote}

\subsection*{General Education Student Learning Goals}

	Students completing courses in this subarea shall encounter the following learning goals:

\begin{enumerate}
	\item Examine problems, issues, and themes in the social sciences in greater depth; in a variety of cultural, historical, and geographical contexts; and from different disciplinary and interdisciplinary perspectives.
	\item Analyze and critically evaluate the application of social science concepts and theories to particular historical, contemporary, and future problems or themes, such as economic and environmental sustainability, globalization, poverty, and social justice.
	\item Analyze and critically evaluate constructs of cultural differentiation, including ethnicity, gender, race, class, and sexual orientation, and their effects on the individual and society.
	\item Apply theories and concepts from the social sciences to address historical, contemporary, and future problems confronting communities at different geographical scales, from local to global.
\end{enumerate}


\section*{University Student Policies}

In accordance with UPS 300.004, students must be familiar with certain policies applicable to all courses. Please review these policies as needed and visit the Cal State Fullerton website for \texttt{\href{https://fdc.fullerton.edu/teaching/student-info-syllabi.html}{syllabus policies}} for links to the following information:

\begin{enumerate}
    \item   University learning goals and program learning outcomes.
    \item	Learning objectives for each General Education (GE) category.
    \item	Guidelines for appropriate online behavior (netiquette).
    \item	Students’ rights to accommodations for documented special needs.
    \item   Campus student support measures, including Counseling \& Psychological Services, Title IV and Gender Equity, Diversity Initiatives and Resource Centers, and Basic Needs Services.
    \item	Academic integrity (refer to UPS 300.021).
    \item	Actions to take during an emergency.
    \item	Library services information.
    \item	Student Information Technology Services, including details on technical competencies and resources required for all students.
    \item	Software privacy and accessibility statements.
\end{enumerate}


\subsection*{Academic Integrity}
Students are expected to adhere to the highest standards of academic integrity. Any student found to have engaged in academic dishonesty will be subject to the sanctions described in the \href{https://www.fullerton.edu/senate/publications_policies_resolutions/ups/UPS%20300/UPS%20300.021.pdf}{Academic Dishonesty Policy} (UPS 300.021). Academic dishonesty includes, but is not limited to, cheating, plagiarism, fabrication, facilitating academic dishonesty, and submitting previously graded work without prior authorization. Students are expected to be familiar with the university's policy on academic dishonesty and to adhere to this policy in all aspects of this course. Any student who has questions about the policy should ask the professor for clarification.

\section*{Course Student Policies}

\subsection*{Course Communication}
All course announcements and communications will be sent via \emph{Canvas} and university email. Students are responsible for regularly checking their \emph{Canvas} notifications and email. Students are also responsible for ensuring that their \emph{Canvas} notifications are set to receive messages from the course. Students are expected to check \emph{Canvas} and their email at least once daily.

\subsection*{Participation}

Students are expected to participate in all course activities. This includes completing all assigned readings, watching all assigned videos, and participating in all discussions. Students are expected to participate in discussions in a professional and respectful manner. Students are expected to be familiar with the university policy on netiquette and to adhere to this policy in all aspects of this course. Any student who has questions about the policy should ask the professor for clarification. 

\begin{quote}Netiquette refers to a set of behaviors that are appropriate for online activity (e.g., social media, email, discussions, presentations). All personnel at Cal State Fullerton are expected to demonstrate appropriate online behavior at all times. A good summary of netiquette can be found in the \href{https://canvashelp.fullerton.edu/m/Student/l/1336786-student-what-is-netiquette}{CSUF Canvas self-help guides}, which adapts ten rules to the online course situation from the website for the book \href{http://www.albion.com/netiquette/corerules.html}{Netiquette by Virginia Shea} and other sources referenced at the bottom of the guide.\end{quote}


\subsection*{Artificial Intelligence Policy}

\subsubsection*{Definitions of Generative AI}

\noindent For the purposes of this course, generative AI refers to artificial intelligence systems capable of producing human-like text, images, or other content. This includes, but is not limited to:

\begin{itemize}
    \item Large language models (e.g., GPT-3, GPT-4)
    \item Text-to-image generators (e.g., DALL-E, Midjourney)
    \item AI-powered writing assistants (e.g., ChatGPT, Claude)
    \item Automated content generators
\end{itemize}

\subsubsection*{AI Use Policy}

In this course, the use of AI is permitted and encouraged as a learning tool, with the following guidelines:

\begin{itemize}
    \item \textbf{Allowed}: Using AI to generate feedback on writing assignments, such as grammar suggestions, style improvements, or additional insights.
    \item \textbf{Allowed}: Using AI to generate ideas or prompts for discussions, essays, or other assignments.
    \item \textbf{Allowed}: Using AI to assist in research, such as summarizing articles, generating citations, or providing additional context.
    \item \textbf{Not Allowed}: Submitting AI-generated content as your own work without proper attribution.
    \item \textbf{Not Allowed}: Using AI to complete assignments that require original thought, analysis, or interpretation.
    \item \textbf{Not Allowed}: Using AI to generate responses in discussions or other interactive activities where personal engagement is required.
    \item \textbf{Not Allowed}: Using AI to take quizzes, exams, or other assessments that are meant to evaluate your individual understanding and skills.
    \item \textbf{Not Allowed}: Using AI to engage in academic dishonesty, such as plagiarism, cheating, or misrepresentation of your work.
\end{itemize}

\subsubsection*{Rationale for AI Policy}

This AI policy is designed to align with our course objectives:

\begin{enumerate}
    \item It supports the examination of public administration theories by encouraging critical engagement with AI feedback.
    \item It enhances literature review skills by allowing AI to provide additional perspectives on annotations and syntheses.
    \item It improves writing skills by providing an additional source of feedback and encouraging revision.
    \item It fosters critical thinking by requiring students to evaluate and incorporate AI feedback thoughtfully.
    \item It contributes to professional development by familiarizing students with AI tools they may encounter in their public administration careers.
\end{enumerate}

\subsubsection*{Guidance for Students on AI Use}

\begin{itemize}
    \item When using AI for feedback, always cite it as a source. For example: ``ChatGPT (Version X.X) [AI model]. OpenAI. Feedback received on [Date].''
    \item Be critical of AI-generated content. AI can make mistakes or provide biased information.
    \item Use AI as a tool to enhance your learning, not as a substitute for your own critical thinking and analysis.
    \item We will discuss ethical AI use and its implications for public administration during our course.
\end{itemize}

\subsubsection*{Repercussions for Policy Breaches}

\begin{itemize}
    \item Suspected misuse of AI (e.g., submitting AI-generated content as your own without proper attribution) will be addressed on a case-by-case basis.
    \item Detection methods may include inconsistencies in writing style, unusual phrasing, or content that doesn't align with the student's demonstrated knowledge and skills.
    \item Consequences for policy breaches may range from a required revision of the assignment to more severe academic integrity penalties, such as dismissal from the MPA program, depending on the nature and extent of the misuse.
\end{itemize}
\noindent Remember, the goal of this policy is to enhance your learning experience and prepare you for a future where AI will likely play a significant role in public administration. Use these tools responsibly and ethically to support your academic and professional growth.

\subsection*{Due Dates}
If you have concerns about meeting assignment deadlines, please get in touch with the professor in advance to discuss potential accommodation. This is a fast-paced course, and late assignments will deducted a half letter grade for each day (24 hours) they are late.

\subsection*{Alternative Procedures for Submitting Work}
Students are expected to submit all assignments via \emph{Canvas}. If you cannot submit an assignment via \emph{Canvas}, please get in touch with the professor to discuss alternative submission procedures.

\subsection*{Extra Credit}
There are no extra credit assignments in this course. 

\section*{Course Delivery}

This course will be delivered asynchronously online via \emph{Canvas}. Students are expected to log on to \emph{Canvas} at least once daily to check for announcements and updates. Students are also expected to check their university email at least once daily.

\section*{Course Structure}

This course is divided into 10 modules. Each module will include a video lecture, assigned readings, a discussion, and a writing assignment. 
\section*{Course Requirements}

\subsection*{Video Lectures and Quizzes}

Each module will include a video lecture. Students are expected to watch each video lecture and complete the corresponding quiz. Video lectures will be available on \emph{Canvas} and on YouTube. Quizzes will be administered via \emph{Canvas}.

\subsection*{Readings}

Each module will include assigned readings. Students are expected to complete all assigned readings. Readings consist of the textbook material covered in each module and additional readings posted to \emph{Canvas}.

\subsection*{Discussions}

Each week will include a discussion. Students are expected to participate in all discussions. Discussions will be administered via \emph{Canvas}. Instructions for each discussion will be posted to \emph{Canvas}.

\subsection*{Writing Assignments}
Over the course of this term, you will complete a Policy Brief Project, a scaffolded assignment that builds on the topics and concepts covered each week. This project challenges you to analyze a real-world issue in public administration and propose actionable solutions. The project is broken into four components: identifying the problem (Week 1), analyzing the context (Week 2), developing recommendations (Week 3), and finalizing the brief (Week 4). Each step provides structured guidance to help you apply course material effectively and create a professional, evidence-based document. By the end of the course, you will have a polished, 6-8 page policy brief that demonstrates your ability to synthesize research, critically analyze issues, and communicate recommendations clearly. Detailed instructions and rubrics for each stage will be provided in Canvas.

\subsection*{Quizzes}
Each module will include a quiz. Quizzes will be administered via \emph{Canvas}. Quizzes will cover the material presented in the video lectures and assigned readings for each module.

\section*{Grades}

\subsection*{Grading Scale and Grade Weights}  
The grading scale is shown in Table~\ref{tab:grading-scale}. Grades will be given based on Table~\ref{tab:grade-weights} weights.

\begin{table}[ht]
\centering
\caption{Grading Scale}
\begin{tabular}{llll}
\toprule
\textbf{Grade} & \textbf{Percentage} & \textbf{Grade} & \textbf{Percentage} \\ \hline
        A+ & 98.0 -- 100  & C+ & 78.0 -- 79.9 \\
        A  & 92.0 -- 97.9 & C  & 72.0 -- 77.9 \\
        A- & 90.0 -- 91.9 & C- & 70.0 -- 71.9 \\
        B+ & 88.0 -- 89.9 & D+ & 68.0 -- 69.9 \\
        B  & 82.0 -- 87.9 & D  & 62.0 -- 67.9 \\
        B- & 80.0 -- 81.9 & D- & 60.0 -- 61.9 \\
           &              & F  & Below 59.9   \\
\bottomrule
\end{tabular}
\label{tab:grading-scale}
\end{table}

\begin{table}[ht]
    \centering
    \caption{Grade Weights}
    \begin{tabular}{ll}
        \toprule
    \textbf{Assignment} & \textbf{Percentage} \\
    \midrule
    Video Lectures and Quizzes & 30\% \\
    Discussions & 15\% \\
    Writing Assignment (Policy Brief) & 55\% \\
    \bottomrule
    \end{tabular}
    \label{tab:grade-weights}
\end{table}

\subsection*{Grade Disputes}

If you have a question about a grade, please contact the professor via email or \emph{Canvas} message. Please include a detailed explanation of your question and a copy of the assignment in question. Please allow up to 48 hours for a response. 

\section*{Course Schedule}

\subsection*{Week 1: Introduction and Foundations (12/22 - 12/28)}

\begin{itemize}
    \item \textbf{Module 1:} Course Introduction and Overview
        \begin{itemize}
            \item Introduction video
            \item What is Public Administration?
        \end{itemize}
    \item \textbf{Module 2:} The Foundations of Public Administration
        \begin{itemize}
            \item Video 1: Basic Concepts
            \item Video 2: Historical Context
        \end{itemize}
    \item \textbf{Discussion:} Importance of Public Administration
    \item \textbf{Writing Assignment:} Policy Brief Project: Identifying the Problem
\end{itemize}

\subsection*{Week 2: Government Functions and Organizational Theory (12/29 - 1/4)}
\begin{itemize}
    \item \textbf{Module 3:} Government Functions
        \begin{itemize}
            \item Video 1: What Government Does
            \item Video 2: How Government Functions
        \end{itemize}
    \item \textbf{Module 4:} Organizational Theory
        \begin{itemize}
            \item Video 1: Basics of Organizational Theory
            \item Video 2: Application in Public Administration
        \end{itemize}
    \item \textbf{Module 5:} The Executive Branch and Organization Problems
    \begin{itemize}
        \item Video 1: Structure of the Executive Branch
        \item Video 2: Common Organizational Problems
    \end{itemize} 
    \item \textbf{Discussion:} Real-world examples of government functions
    \item \textbf{Writing Assignment:} Policy Brief Project: Analyzing the Context
\end{itemize}

\subsection*{Week 3: Human Capital and Decision Making (1/5 - 1/11)}
\begin{itemize}
    \item \textbf{Module 6:} Human Capital in Government
        \begin{itemize}
            \item Video 1: The Civil Service
            \item Video 2: Human Capital Management
        \end{itemize}
    \item \textbf{Module 7:} Decision Making and Budgeting
        \begin{itemize}
            \item Video 1: Decision Making in Public Administration
            \item Video 2: Budgeting Process
        \end{itemize}
    \item \textbf{Discussion:} Challenges in managing human capital in public sector
    \item \textbf{Writing Assignment:} Policy Brief Project: Developing Recommendations
\end{itemize}

\subsection*{Week 4: Implementation, Performance, and Accountability (1/12 - \emph{Friday 1/1})}
\begin{itemize}
    \item \textbf{Module 8:} Implementation and Performance
        \begin{itemize}
            \item Video 1: Strategies for Effective Implementation
            \item Video 2: Measuring Performance in Public Sector
        \end{itemize}  
    \item \textbf{Module 9:} Regulation and the Courts
        \begin{itemize}
            \item Video 1: Role of Regulation
            \item Video 2: Public Administration and the Judiciary
        \end{itemize}
    \item \textbf{Module 10:} Accountability and Oversight
        \begin{itemize}
            \item Video 1: Concepts of Accountability
            \item Video 2: Mechanisms for Oversight
        \end{itemize}
    \item \textbf{Discussion:} Balancing regulation and innovation
    \item \textbf{Writing Assignment:} Policy Brief Project: Finalizing the Brief
    \item \textbf{Course Wrap-Up:} Summary video, feedback, and next steps
\end{itemize}

\end{document}